Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-08-22 cc/variants.tex
a few things here and there

In \msc{}, the goal is to output a clustering which best summarizes (or agrees with) the several
given input clusterings of the same set of objects.  Motivations include robustness ---by using an
ensemble of clusterings from diverse methods--- and privacy ---if the clusterings were computed by
different parties each considering only a subset of the objects attributes. We can build the
complete graph of these objects, with weights set to the fraction of clusterings that place two
objects in different clusters, thus representing a kind of distance in the space of clusterings.  As
first show by \textcite{Gionis2007}, finding the optimal clustering is therefore an instance of
\pcc{} where the weights obey the triangular inequality. They give a deterministic $3$-approximation
using the \regionGrow{} method. Later \textcite{Bonizzoni2008} show that
the minimization version is \APXh{}, even when the input is made of three clusterings and give a
combinatorial $\nicefrac{4}{5}$-approximation for the maximization problem. Experimental evaluations are
conducted by \textcite{Bertolacci07} and \textcite{Filkov08}. The former describe a scalable
approach that first samples a small portion of the data, runs a (potentially computationally
expensive) approximation algorithm and finally augment the resulting partition by adding to it the
unsampled nodes one by one.  Experiments confirm that the running time is greatly improved compared
with the linear program methods while the resulting objective value is essentially the same. Note,
however, that LP methods can be applied in practice thanks to some tricks~\autocite{ConsensusLP10}.
If we have $k$ input clusterings $\cluster^1,\ldots,\cluster^k$ and we parameterized the problem by
$t$, which is the sum over the input clusterings of the number of pairs of objects that are clustered
differently by a solution $\cluster^\star$ and $\cluster^i$, then there is a polynomial algorithm
running in $O(4.24^{\nicefrac{t}{k}}\cdot \nicefrac{t}{k}^3 +
kn^2)$~\autocite{parameterizedConsensus14}.

>>>>

In \msc{}, the goal is to output a clustering which best summarizes (or agrees with) the several
given input clusterings of the same set of objects.  Motivations include robustness ---by using an
ensemble of clusterings from diverse methods--- and privacy ---if the clusterings were computed by
different parties each considering only a subset of the objects attributes. We can build the
complete graph of these objects, with weights set to the fraction of clusterings that place two
objects in different clusters, thus representing a kind of distance in the space of clusterings.  As
first show by \textcite{EarlyConsensusClustering03}} , finding the optimal clustering is therefore
an instance of \pcc{} where the weights obey the triangular inequality. \textcite{Gionis2007} give a
deterministic $3$-approximation using the \regionGrow{} method. Later \textcite{Bonizzoni2008} show that
the minimization version is \APXh{}, even when the input is made of three clusterings and give a
combinatorial $\nicefrac{4}{5}$-approximation for the maximization problem. Experimental evaluations are
conducted by \textcite{Bertolacci07} and \textcite{Filkov08}. The former describe a scalable
approach that first samples a small portion of the data, runs a (potentially computationally
expensive) approximation algorithm and finally augment the resulting partition by adding to it the
unsampled nodes one by one.  Experiments confirm that the running time is greatly improved compared
with the linear program methods while the resulting objective value is essentially the same. Note,
however, that LP methods can be applied in practice thanks to some tricks~\autocite{ConsensusLP10}.
If we have $k$ input clusterings $\cluster^1,\ldots,\cluster^k$ and we parameterized the problem by
$t$, which is the sum over the input clusterings of the number of pairs of objects that are clustered
differently by a solution $\cluster^\star$ and $\cluster^i$, then there is a polynomial algorithm
running in $O(4.24^{\nicefrac{t}{k}}\cdot \nicefrac{t}{k}^3 +
kn^2)$~\autocite{parameterizedConsensus14}.
